The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-30 manuscript/acronyms.tex
use short/single/long options in acro

\DeclareAcronym{EV}{short=EV,long=Extracellular Vesicle}
\DeclareAcronym{SVM}{long=Support Vector Machine}
\DeclareAcronym{ROC}{long=Receiver Operating Characteristic}
\DeclareAcronym{KNN}{long=K Nearest Neighbors}
\DeclareAcronym{SRA}{long=Sequence Read Archive}
\DeclareAcronym{PRG2}{short=\textit{PRG2},long=Proteoglycan 2, bone marrow}
\DeclareAcronym{FPKM}{long=Fragments Per Kilobase of exon per Million reads}
\DeclareAcronym{CSH1}{short=\textit{CSH1},long=chorionic somatomammotropin hormone 1}
\DeclareAcronym{CSH2}{short=\textit{CSH2},long=chorionic somatomammotropin hormone 2}
\DeclareAcronym{CSHL1}{short=\textit{CSHL1},long=chorionic somatomammotropin hormone-like 1}
\DeclareAcronym{GH2}{short=\textit{GH2},long=growth hormone 2}
\DeclareAcronym{CEA}{long=carcinoembryonic antigen}
\DeclareAcronym{HSD3B1}{short=\textit{HSD3B1},long=3-β Hydroxysteroid dehydrogenase 1}
\DeclareAcronym{GSE}{long=Gene Set Enrichment}
\DeclareAcronym{OU}{long=Ornstein-Uhlenbeck}
\DeclareAcronym{OUCH}{long=\ac{OU} Comparative Hypotheses}
\DeclareAcronym{TSI}{long=Tissue Specificity Index}
\DeclareAcronym{SRA}{long=Sequence Read Archive}
\DeclareAcronym{GH}{long=Growth Hormone}
\DeclareAcronym{PSG}{long=Pregnancy-Specific Glycoprotein}
\DeclareAcronym{PAG}{long=Pregnancy-Associated Glycoprotein}
\DeclareAcronym{GO}{long=Gene Ontology}
\DeclareAcronym{FDR}{long=False Discovery Rate}

>>>>

\DeclareAcronym{EV}{short=EV,long=Extracellular Vesicle}
\DeclareAcronym{SVM}{long=Support Vector Machine}
\DeclareAcronym{ROC}{long=Receiver Operating Characteristic}
\DeclareAcronym{KNN}{long=K Nearest Neighbors}
\DeclareAcronym{SRA}{long=Sequence Read Archive}
\DeclareAcronym{CEA}{long=carcinoembryonic antigen}
\DeclareAcronym{GSE}{long=Gene Set Enrichment}
\DeclareAcronym{OU}{long=Ornstein-Uhlenbeck}
\DeclareAcronym{OUCH}{long=\ac{OU} Comparative Hypotheses}
\DeclareAcronym{TSI}{long=Tissue Specificity Index}
\DeclareAcronym{SRA}{long=Sequence Read Archive}
\DeclareAcronym{GH}{long=Growth Hormone}
\DeclareAcronym{PSG}{long=Pregnancy-Specific Glycoprotein}
\DeclareAcronym{PAG}{long=Pregnancy-Associated Glycoprotein}
\DeclareAcronym{GO}{long=Gene Ontology}
\DeclareAcronym{FDR}{long=False Discovery Rate}
\DeclareAcronym{gsea}{short=GSEA,long=gene set enrichment analysis}
\DeclareAcronym{FPKM}{long=Fragments Per Kilobase of exon per Million reads}
\DeclareAcronym{HSD3B1}{short=\textit{HSD3B1},long={hydroxy-δ-5-steroid dehydrogenase, 3 β- and steroid δ-isomerase 1},first-style=reversed,single={\textit{HSD3B1} (hydroxy-δ-5-steroid dehydrogenase, 3 β- and steroid δ-isomerase 1)}}
\DeclareAcronym{CSH1}{short=\textit{CSH1},long={chorionic somatomammotropin hormone 1},first-style=reversed,single={\textit{CSH1} (chorionic somatomammotropin hormone 1)}}
\DeclareAcronym{CSH2}{short=\textit{CSH2},long={chorionic somatomammotropin hormone 2},first-style=reversed,single={\textit{CSH2} (chorionic somatomammotropin hormone 2)}}
\DeclareAcronym{CSHL1}{short=\textit{CSHL1},long={chorionic somatomammotropin hormone like 1},first-style=reversed,single={\textit{CSHL1} (chorionic somatomammotropin hormone like 1)}}
\DeclareAcronym{GH2}{short=\textit{GH2},long={growth hormone 2},first-style=reversed,single={\textit{GH2} (growth hormone 2)}}
\DeclareAcronym{PRG2}{short=\textit{PRG2},long={proteoglycan 2, pro eosinophil major basic protein},first-style=reversed,single={\textit{PRG2} (proteoglycan 2, pro eosinophil major basic protein)}}
\DeclareAcronym{CRH}{short=\textit{CRH},long={corticotropin releasing hormone},first-style=reversed,single={\textit{CRH} (corticotropin releasing hormone)}}
\DeclareAcronym{KISS1}{short=\textit{KISS1},long={KiSS-1 metastasis-suppressor},first-style=reversed,single={\textit{KISS1} (KiSS-1 metastasis-suppressor)}}
\DeclareAcronym{PAPPA}{short=\textit{PAPPA},long={pappalysin 1},first-style=reversed,single={\textit{PAPPA} (pappalysin 1)}}
\DeclareAcronym{ADAM12}{short=\textit{ADAM12},long={ADAM metallopeptidase domain 12},first-style=reversed,single={\textit{ADAM12} (ADAM metallopeptidase domain 12)}}
\DeclareAcronym{ANXA1}{short=\textit{ANXA1},long={annexin A1},first-style=reversed,single={\textit{ANXA1} (annexin A1)}}
\DeclareAcronym{ANXA2}{short=\textit{ANXA2},long={annexin A2},first-style=reversed,single={\textit{ANXA2} (annexin A2)}}
\DeclareAcronym{ANXA5}{short=\textit{ANXA5},long={annexin A5},first-style=reversed,single={\textit{ANXA5} (annexin A5)}}
\DeclareAcronym{S100A11}{short=\textit{S100A11},long={S100 calcium binding protein A11},first-style=reversed,single={\textit{S100A11} (S100 calcium binding protein A11)}}
\DeclareAcronym{S100A10}{short=\textit{S100A10},long={S100 calcium binding protein A10},first-style=reversed,single={\textit{S100A10} (S100 calcium binding protein A10)}}
\DeclareAcronym{LGALS1}{short=\textit{LGALS1},long={galectin 1},first-style=reversed,single={\textit{LGALS1} (galectin 1)}}
\DeclareAcronym{LAMC1}{short=\textit{LAMC1},long={laminin subunit γ 1},first-style=reversed,single={\textit{LAMC1} (laminin subunit γ 1)}}
\DeclareAcronym{LUM}{short=\textit{LUM},long={lumican},first-style=reversed,single={\textit{LUM} (lumican)}}
\DeclareAcronym{GRB2}{short=\textit{GRB2},long={growth factor receptor bound protein 2},first-style=reversed,single={\textit{GRB2} (growth factor receptor bound protein 2)}}
\DeclareAcronym{RALB}{short=\textit{RALB},long={RAS like proto-oncogene B},first-style=reversed,single={\textit{RALB} (RAS like proto-oncogene B)}}
\DeclareAcronym{ERVFRD-1}{short=\textit{ERVFRD-1},long={endogenous retrovirus group FRD member 1},first-style=reversed,single={\textit{ERVFRD-1} (endogenous retrovirus group FRD member 1)}}
\DeclareAcronym{ERVW-1}{short=\textit{ERVW-1},long={endogenous retrovirus group W member 1},first-style=reversed,single={\textit{ERVW-1} (endogenous retrovirus group W member 1)}}
\DeclareAcronym{MFSD2A}{short=\textit{MFSD2A},long={major facilitator superfamily domain containing 2A},first-style=reversed,single={\textit{MFSD2A} (major facilitator superfamily domain containing 2A)}}
\DeclareAcronym{PRSS16}{short=\textit{PRSS16},long={protease, serine 16},first-style=reversed,single={\textit{PRSS16} (protease, serine 16)}}
\DeclareAcronym{TIMP3}{short=\textit{TIMP3},long={TIMP metallopeptidase inhibitor 3},first-style=reversed,single={\textit{TIMP3} (TIMP metallopeptidase inhibitor 3)}}
\DeclareAcronym{F11R}{short=\textit{F11R},long={F11 receptor},first-style=reversed,single={\textit{F11R} (F11 receptor)}}
\DeclareAcronym{SDC4}{short=\textit{SDC4},long={syndecan 4},first-style=reversed,single={\textit{SDC4} (syndecan 4)}}
\DeclareAcronym{FN1}{short=\textit{FN1},long={fibronectin 1},first-style=reversed,single={\textit{FN1} (fibronectin 1)}}
\DeclareAcronym{ITGB1}{short=\textit{ITGB1},long={integrin subunit β 1},first-style=reversed,single={\textit{ITGB1} (integrin subunit β 1)}}
\DeclareAcronym{ITGB1BP1}{short=\textit{ITGB1BP1},long={integrin subunit β 1 binding protein 1},first-style=reversed,single={\textit{ITGB1BP1} (integrin subunit β 1 binding protein 1)}}
\DeclareAcronym{EREG}{short=\textit{EREG},long={epiregulin},first-style=reversed,single={\textit{EREG} (epiregulin)}}
\DeclareAcronym{UNC93A}{short=\textit{UNC93A},long={unc-93 homolog A (C. elegans)},first-style=reversed,single={\textit{UNC93A} (unc-93 homolog A (C. elegans))}}
\DeclareAcronym{UNC93B1}{short=\textit{UNC93B1},long={unc-93 homolog B1 (C. elegans)},first-style=reversed,single={\textit{UNC93B1} (unc-93 homolog B1 (C. elegans))}}
\DeclareAcronym{WNT5A}{short=\textit{WNT5A},long={Wnt family member 5A},first-style=reversed,single={\textit{WNT5A} (Wnt family member 5A)}}
\DeclareAcronym{IL1RL1}{short=\textit{IL1RL1},long={interleukin 1 receptor like 1},first-style=reversed,single={\textit{IL1RL1} (interleukin 1 receptor like 1)}}
\DeclareAcronym{PLAC1}{short=\textit{PLAC1},long={placenta specific 1},first-style=reversed,single={\textit{PLAC1} (placenta specific 1)}}
\DeclareAcronym{Afp}{short=\textit{Afp},long={α-fetoprotein},first-style=reversed,single={\textit{Afp} (α-fetoprotein)}}
\DeclareAcronym{Gjb2}{short=\textit{Gjb2},long={gap junction protein β 2},first-style=reversed,single={\textit{Gjb2} (gap junction protein β 2)}}
\DeclareAcronym{CD9}{short=\textit{CD9},long={CD9 molecule},first-style=reversed,single={\textit{CD9} (CD9 molecule)}}
